---
title: "CISC HW6"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question1

> Download [the baby name data for 2016](https://storm.cis.fordham.edu/ji/cisc5500/yob2016.txt) . Write a R script that reads this file and plots a bar chart of the 10 most popular names regardless of gender, namely the x-axis shows the 10 names and the y-axis shows the number of babies who have a given name.

#### Preprocessing
In the first part, the script read the text file as the input with the edited column names. After the re-order with both two genders, it select the top 10 rows as the output.
```{r preprocessing}
df <- read.csv('/Users/lordxuzhiyu/Desktop/yob2016.txt', col.names = c('Name', 'Sex', 'Count'))
res <- df[with(df, order(-Count)),]
result <- head(res, 10)
result
```
#### Plot with ggplot2
After that, we use the ggplot2 package to draw the bar chart. The result is below:
```{r plot}
library(ggplot2)

ggplot(result, aes(x = Name, y = Count)) + geom_bar(stat = "identity")
```

## Question 2
> Write a R function that takes a vector (assuming the elements are integers) and returns a vector of only the elements that are multiple of 4 but not multiple of 100.

#### Design
We initalize a vector with a range of integers. Then we just output the result with the condition we want.
```{r vector}
input <- 1:1000
input[((input %% 4) == 0)&((input %% 100) != 0)]
```
